Predicting sales of newly published books

### 2015-08-29 paper.tex
Some corrections adds to @fergunet

  %[Pedro] otro caso a comentar es el paper de Chang2009 sobre: 
  % sales forecasting in printed circuit board industry.
In those cases where historical data is available, classical time series 
forecasting methods can be applied, such as in \cite{Chang2009}, where a hybrid 
model integrating K-mean and fuzzy neural networks to forecast the future sales 
of a printed circuit board is proposed.
A similar method is proposed by Chern et al \cite{Chern2015}, who analyze 
historical data along online reviews, reviewer characteristics and review 
influences to understand how electronic word-of-mouth affects product sales. 
The proposed method is suitable in those sales forecasting problems with abundant %FERGU: _The_ proposed method?    ok
online reviews and historical data.

Taking into account the kind of problem we address in this paper, 
a new product sales prediction for which no historical data is available,
the classical forecasting methods based on time series are not adequate. 
Thus, in this paper the relevant variables in the prediction of sales are determined
using data visualization tools and then, standard data mining software 
to predict sales is used to deduce print-run.
In addition, since publishers need models to explain obtained predictions, 
black box forecasting methods may not be suitable for this problem, so 
models based on rules are tested as an alternative.

@@

Finally, in the literature different error measures can be found to report 
the results obtained using the prediction methods \cite{ChingChin2010,Madsen2008}. 
Those error measurements are also called error functions or cost functions. 
%One of the most commonly used is the mean absolute error (see equation \ref{eq:MAE}).
In any case, we recommend using widely accepted standard 
equations\footnote{http://www.gepsoft.com/gxpt4kb/Chapter10/Section3/Introduction.htm} %FERGU: mejor tratar esto como una referencia, ya que es un texto
in order to compare obtained results with those presented in other research 
papers using other methods.
That is why different standard error measurements (Equations \ref{eq:MAE} to \ref{eq:RRSE}), 
implemented in tools like Weka\footnote{http://wiki.pentaho.com/display/DATAMINING} \cite{Witten2011} 
or R\footnote{https://www.otexts.org/fpp/2/5} \cite{Hyndman2013}, are proposed.
Specifically, in order to compute the forecasting errors of the different methods, 
%FERGU: quitar este salto de linea y unirlo al párrafo de arriba.    ok
Mean absolute error (MAE), Root mean squared error (RMSE), Relative absolute 
error (RAE) and Root relative squared error (RRSE) have been selected:

@@

As future work, it would be interesting comparing the obtained forecasting results 
with other methods based on soft-computing, such as genetic programming or fuzzy logic.
Moreover, as default parameters have been used for proposed forecasting methods,
it would be of interest carrying out some parameter tuning procedure in order to
improve obtained results.

@@

@@

\end{document}

>>>>

  %[Pedro] otro caso a comentar es el paper de Chang2009 sobre: 
  % sales forecasting in printed circuit board industry.
In those cases where historical data is available, classical time series 
forecasting methods can be applied, which is what they do in \cite{Chang2009}, where a hybrid 
model integrating K-means and fuzzy neural networks to forecast the future sales 
of a printed circuit board is proposed.
A similar method is proposed by Chern et al \cite{Chern2015}, who analyze 
historical data along online reviews, reviewer characteristics and review 
influences to understand how electronic word-of-mouth affects product sales. 
The proposed method is suitable in those sales forecasting problems with abundant %FERGU: _The_ proposed method?    ok
online reviews and historical data.

Taking into account the kind of problem we address in this paper,
prediction of sales of 
a new product for which no historical data is available,
the classical forecasting methods based on time series are not
adequate, although they can obviously be used once the book has been
for sale. 
Thus, in this paper the relevant variables in the prediction of sales are determined
using data visualization tools and then, standard data mining software 
to predict sales is used to deduce print-run.
In addition, since publishers need models to explain obtained predictions, 
black box forecasting methods may not be suitable for this problem, so 
models based on rules are tested as an alternative.

@@

Finally, in the literature different error measures can be found to report 
the results obtained using the prediction methods \cite{ChingChin2010,Madsen2008}. 
Those error measurements are also called error functions or cost functions. 
%One of the most commonly used is the mean absolute error (see equation \ref{eq:MAE}).
In any case, we recommend using widely accepted standard 
equations\footnote{http://www.gepsoft.com/gxpt4kb/Chapter10/Section3/Introduction.htm}
% FERGU: mejor tratar esto como una referencia, ya que es un texto
% Efectivamente- JJ
in order to compare obtained results with those presented in other research 
papers using other methods.
That is why different standard error measurements (Equations \ref{eq:MAE} to \ref{eq:RRSE}), 
implemented in tools like Weka\footnote{http://wiki.pentaho.com/display/DATAMINING} \cite{Witten2011} 
or R\footnote{https://www.otexts.org/fpp/2/5} \cite{Hyndman2013}, are
proposed.
% no se deben usar footnotes donde debiera haber referencias. - JJ
Specifically, in order to compute the forecasting errors of the different methods, 
%FERGU: quitar este salto de linea y unirlo al párrafo de arriba.    ok
Mean absolute error (MAE), Root mean squared error (RMSE), Relative absolute 
error (RAE) and Root relative squared error (RRSE) have been selected:

@@

As future work, it would be interesting to compare the obtained forecasting results 
with other methods based on soft-computing, such as genetic programming or fuzzy logic.
Moreover, as default parameters have been used for proposed forecasting methods,
it would be of interest carrying out some parameter tuning procedure in order to
improve obtained results.

@@

Finally, there are some variables over which the published has some
control once the book has been published, such as the initial print
run or the books given out as gifts to reviewers or what proportion is
going to be sent to each possible point of sale. This can be
incorporated into an optimization model that optimizes those values to
obtain desired sales. This is left as future work.

@@

\end{document}
%%% Local Variables:
%%% ispell-local-dictionary: "english"
%%% End:
